Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features

### 2016-12-14 paper/structureScene.tex
upload biography

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/lafay}}]{Gr\'egoire Lafay} was born in Paris, France, in 1990. He received in 2011 the B.S. degree in Acoustic from the University Pierre and Marie Curie (UPMC), Paris, France, and the B.S. degree in Musicology from the Sorbonne University, Paris, France. He received his M.S. degree in acoustics, signal processing and musical informatics (ATIAM) from the University Pierre and Marie Curie and the IRCAM laboratory, Paris, France, in 2013. Since 2013, he is a Ph.D student at Irccyn, a French laboratory dedicated to cybernetics. His current research interests include acoustic scene similarity and classification, as well as acoustic scene perception. 
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1.25in,height=1.25in,clip,keepaspectratio]{gfx/lagrange}}]{Mathieu Lagrange} is a CNRS research scientist at Irccyn, a French laboratory dedicated to cybernetics. He obtained his PhD in computer science at the University of Bordeaux in 2004, and visited several institutions, in Canada (University of Victoria, McGill University) and in France (Orange Labs, Telecom ParisTech, Ircam). His research focuses on machine listening algorithms applied to the analysis of musical and environmental audio.
\end{IEEEbiography}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/lostanlen}}]{Vincent Lostanlen} was born in 1992. He received his M.S. degree in acoustics, signal processing, and musical informatics (ATIAM) from the Universit\'{e} Pierre et Marie Curie and the Ircam in Paris, France. Since 2013, he is a PhD student at ENS in Paris.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/lafay}}]{Gr\'egoire Lafay} was born in Paris, France, in 1990. He received in 2011 the B.S. degree in Acoustic from the University Pierre and Marie Curie (UPMC), Paris, France, and the B.S. degree in Musicology from the Sorbonne University, Paris, France. He received his M.S. degree in acoustics, signal processing, and musical informatics (ATIAM) from the Universit\'{e} Pierre and Marie Curie and the Ircam in Paris, France, in 2013. Since 2013, he is a Ph.D student at IRCCyN, a French laboratory dedicated to cybernetics. His current research interests include acoustic scene similarity and classification, as well as acoustic scene perception. 
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1.25in,height=1.25in,clip,keepaspectratio]{gfx/lagrange}}]{Mathieu Lagrange} is a CNRS research scientist at IRCCyN, a French laboratory dedicated to cybernetics. He obtained his PhD in computer science at the University of Bordeaux in 2004, and visited several institutions in Canada (University of Victoria, McGill University) and in France (Orange Labs, Telecom ParisTech, Ircam). His research focuses on machine listening algorithms applied to the analysis of musical and environmental audio.
